Evolving Challenges and Solutions in Network Management

### 2024-11-12 paper.tex
added agent image

\textbf{Generative AI}

Generative AI (GenAI) is set to transform network management by incorporating AI systems that follow the autonomic networking principles outlined RFC7575.

@@

Agentic architectures, characterized by AI agents that autonomously discover and utilize tools provide dynamic interactions with complex systems, effectively adapting to changes that static codebases cannot. AI agents are capable of decomposing user intents into executable individual steps and can interact autonomously with other systems through well-known interfaces (e.g., Network and Management APIs). Agents can further federate and specialize in multi-agent systems, which improve on challenges such as hallucinations, specialization, and scalability. The interest in multi-agent systems was reflected during the past IETF 121 side meeting, as detailed in the ai4network agenda \cite{ai4network-agenda}.

>>>>

\textbf{AI Agents}

Zero-shot LLMs are are already used to make operator insights more accessible, to streamline incident management or to generate task-specific code from natural language queries. As the industry progresses in the GenAI path, agentic architectures will be integrated into network AI systems, adhering to the autonomic networking principles specified in RFC7575.

@@

Agentic systems are characterized by AI agents that are capable of decomposing user intents into executable individual steps and can interact autonomously with other systems through well-known interfaces (e.g., Network and Management APIs). Agents can further federate and specialize in multi-agent systems, which improve on challenges such as hallucinations, specialization, and scalability. The interest in multi-agent systems was reflected during the past IETF 121 side meeting, as detailed in the ai4network agenda \cite{ai4network-agenda}.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{figs/agent.png}
  \caption{Agentic System Architecture}
  \label{fig:agent_architecture}
\end{figure}
